---
title: "Stat139_Presentation"
---
title: "statsprojtwo"
output: html_document
date: "2023-03-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This block just installs the necessary packages. Only run it once, when you first start the environment.

```{r cars, eval=FALSE}
# If necessary, install packages
install.packages('sgt')
install.packages('ggplot2')
install.packages("Dict")
install.packages("gridExtra")
install.packages("moments")
```

## Hyperparameters

Here we set each value that we will consider for our SGT distributions.

```{r}
library(sgt)
library(ggplot2)
library(Dict)
library(moments)
library(gridExtra)
```

```{r}
# These are all set to pre-determined values
mu = 0
sigma = 1
p = 2
sample_size = 5000
# List of lambdas and qs to vary
lambdas = c(0, .1, .5, .99)
qs = c(.5, 2, 10, 100)
ns = seq(1, 30, 1)
# Stores the S-W statistic for each choice of parameters for each n.
df <- data.frame (
  lambda = c(0),
  q = c(0),
  n = c(0),
  W = c(0),
  p_val = c(0),
  skewness = c(0),
  kurt = c(0),
  bias = c(0)
)
# Stores the means for each run with a key of the form "[lambda]_[q]_[n]" (for lambda, the 0 is included, so do '0.99', not '.99')
means_dict = Dict$new(Test = 1:5000)
```

## Simulation Code

This code is used to run the simulation. This will be the longest block, so only run it when you need to!

Otherwise, simply load the dataframe clt_data.csv (the block below this one).

```{r pressure, cache = TRUE}
# For each lambda, q, and n value:
for (lambda in lambdas) {
  for (q in qs) {
    for (n in ns) {
      # Calculate sample_size sample means
      means <- c()
      for (i in 1:sample_size) {
        data <- rsgt(n, mu = mu, sigma = sigma, lambda = lambda, p = 2, q = q, mean.cent = FALSE, var.adj = FALSE)
        means <- append(means, mean(data))
      }
      
      qq_plot <- qqnorm(means,  main = paste("Q-Q Plot of Simulated Averages with q = ", q, ", n = ", n, ", and lambda =", lambda))
      qqline(means)
      name <- sprintf("%s_%s_%s", lambda, q, n)
      means_dict[name] <- means
      stat <- shapiro.test(means)
      skew <- skewness(means)
      kurt <- kurtosis(means)
      bias <- mean(means)
      df[nrow(df) + 1,] <- c(lambda, q, n, stat[1], stat[2], skew, kurt, bias)
      
      # plot= ggplot() + geom_histogram(aes(means), bins = 20)
      # name <- sprintf("%s_%s_%s.pdf", lambda, q, n)
      # ggsave(plot,file=name)
    }
  }
}
```

```{r}
df
```

```{r, eval=FALSE}
grid.arrange(qq_plots, nrow = 16)

grid.newpage()
n_plots <- length(qq_plots)
for (i in 1:n_plots) {
  grid.draw(qq_plots[i])
  if (i %% 10 == 0) {
    grid.newpage()
  }
}

df
```


```{r}
qs_now <- c(2, 10, 100)
i = 1
colors <- c("red", "blue", "green", "yellow", "purple", "orange", "brown", "black")
leg_names = c("W = .95")
plot(ns, rep(c(.95), times=length(ns)), lty=i, ylim=c(.85,1), col=colors[i])
lines(ns, rep(c(.95), times=length(ns)), lty=i, col=colors[i])
i <- i + 1
for (lambda in lambdas) {
  for (q in qs_now) {
    df_now <- df[df$q == q & df$lambda == lambda, ]
    #points(df_now$n, df_now$W, pch="*")
    lines(df_now$n, df_now$W, lty=i, col=colors[i])
    leg_names <- append(leg_names, sprintf("q = %s, lambda = %s", q, lambda))
    i <- i + 1
  }
}
legend("bottomright", legend=leg_names,
       col=colors, lty=1:i, cex=0.8)
```


